---
title: "Plotting a Selected Column with All Possible Columns of a Data Frame"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
  
  
# Scatter Plot All
  
  A function `scatter_plot_all` that creates many scatter plots with same attribute on every plot on the x-axis and a different attribute for every plot on the y-axis. `mtcars` dataset is used to visually illustrate how to use the function in different ways. 



```{r, include = FALSE}
knitr::opts_chunk$set( echo = TRUE,
                       fig.width=6,
                       fig.height=6,
                       fig.align = "center"
)
```

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(beyondggplot)
```

```{r}
# displaying the top values in mtcars

head(mtcars)

```


```{r }
#looking at the structure of mtcars

str(mtcars)

```

```{r }
# converting gears to a factor

mtcars$gear <- as.factor(mtcars$gear)

# converting cyl to a factor

mtcars$cyl <- as.factor(mtcars$cyl)

#looking at the new structure of mtcars

str(mtcars)
```


```{r, eval=TRUE}
# the simplest way to use plot_all with 
# first argument is for the datafram 
# second argument "col_x" for the attribute on the x-axis

scatter_plot_all(mtcars, col_x = "mpg")
```


```{r}
# a third argument "col_color" for the attribute determining the color of data point

scatter_plot_all(mtcars, col_x = "mpg", col_color = "cyl")
```


```{r}
# a fourth argument "col_shape" for the attribute determining the shape of data point
scatter_plot_all(mtcars, col_x = "mpg", col_color = "cyl", col_shape = "gear")
```

``` {r}
# a fifth argument "col_size" for the attribute determining the size of data point
scatter_plot_all(mtcars, col_x = "mpg", col_color = "cyl", col_shape = "gear", col_size = "wt")

```

# Hex Plot All

A function `hex_plot_all` that creates many hax plots with same attribute on every plot on the x-axis and a different attribute for every plot on the y-axis. `iris` dataset is used to visually illustrate how to use the function in different ways. 

```{r, eval=TRUE}
# the simplest way to use hex_plot_all with 
# first argument for the datafram 
# second argument "col_x" for the attribute on the x-axis

hex_plot_all(iris, col_x = "Sepal.Length")
```

```{r}
# a third argument "col_color" for the attribute determining the fill color of data point

hex_plot_all(iris, col_x = "Sepal.Length", col_fill = "Species")
```

